\documentclass[8pt,draft]{report}
\usepackage{verbatim}
\begin{document}

\author{Artagnon}
\title{The Definitive Guide to Life behind Squid}
\date{Compiled with \LaTeX{} on \today}
\maketitle

\section{Audience}
Moo

\section{Author's note}
It's frustrating to constantly live behind a HTTP proxy, here at IIT Kharagpur. No IRC, no email, no torrents, no GIT, and probably the worst of all- no SSH. This book initially started out as a small document describing the steps I'd taken to circumbent the system legitimately. However, because I don't like cookbooks, I started explaining the logic behind every step I was taking. The draft eventually evolved into a book for dealing with various types of proxies.

\section{Introduction}
 to enable people to do more than just web browsing and DC++ in a restrictive environment. However, I don't write cookbooks-  I'll explain every decision I've taken along the way to break every program out legitimately. Note, however, that I'm no networking expert. I might therefore have made glaring mistakes- The book is written purely from an engineeer-hacker's perspective and should not be used for academic purposes.

The Squid setup at IIT Kharagpur is especially restrictive and frustrating, which is the reason tools like Corkscrew can't be used to break out\footnote{Yes, I will explain what the setup is and why it's particularly restrictive}. I've written this book for the worst Squid setup, and should hence be adaptable to any setup.

\section{Networking 101}
\input{networking101}
\section{The ``proxy'' primer}
A proxy server is 
\section{Tests}
\input{tests}
\end{document}
